### 2021-09-23 documentos/math.tex
marks

We now turn to find the matrix form of the map $\mathcal{E}$ in order to construct the Choi matrix and the conditions the set of parameters $\{\tau_{\alpha}\}$ need to satisfy in order to $\mathcal{E}$ be considered a quantum channel. By writing the density matrix in vector form $\ket{\rho}=\sum_{\alpha=0}^{3} \alpha_{\alpha} \ket{\sigma_{\alpha}}$, it is easy to show that the matrix form of the map $\mathcal{E}$ may be written as
% 
\begin{equation}
\hat{\mathcal{E}} = \frac{1}{2}\sum_{\alpha=0}^{3} \tau_{\alpha} \dyad{\sigma_{\alpha}},
% \label{Map_Pauli}
\end{equation}
%
where the kets $\ket{\sigma_{\alpha}}$ correspond to the vectorized elements of the Pauli basis and satisfy the usual relation $ \braket{{\sigma_{\alpha}}}{{\sigma_{\alpha'}}} = \tr \left(\sigma_{\alpha}^{\dagger} \sigma_{\alpha'}\right) = 2 ~\delta_{\alpha\alpha'}$. After some steps it is possible to show that the associated Choi matrix reads
% 
\begin{equation}
 \mathcal{D} = \frac{1}{2}\sum_{\alpha=0}^{3} \tau_{\alpha} \sigma_{\alpha} \otimes \sigma_{\alpha}^*.
%  \label{Choi_1}
\end{equation}
% 
Note that $\mathcal{D}$ has the same form as the matrix representation of a random unitary channel whose Kraus operators are given by $K_{\alpha}=\sqrt{\frac{\tau_{\alpha}}{2}}\sigma_{\alpha}$. For the latter case, it has been shown that corresponding eigenvalues read \cite{CHRUSCINSKI20131425}
% 
\begin{equation}
 \lambda_{\beta} = \frac{1}{2}\sum_{\alpha=0}^3H_{\beta\alpha}^{(4)}\tau_{\alpha},
\end{equation}
%
or
% 
\begin{equation}
 \vec{\lambda} = \frac{1}{2}~ H^{(2)}\otimes H^{(2)}\vec{\tau},
\end{equation}
% 
where $H^{(m)}$ is the Hadamard matrix of order \textit{m}, and for $m=2$ reduces to the usual Hadamard matrix.
% 
\begin{equation}
 H^{(2)}=\begin{pmatrix}
        1 & 1\\
        1 & -1\\
    \end{pmatrix}.
 \label{Hadd_Mat}
\end{equation}

@@

\subsubsection{$N$ qubits}
% 
For the case of $N$ qubits, the density matrix may be written as
% 
\begin{equation}
\rho=\sum_{\vec{\alpha}} r_{\vec{\alpha}} \sigma_{\vec{\alpha}}.
% \label{rho2}
\end{equation}
% 
Analogously to the single qubit case, we can define a $N$-qubits Pauli map
% 
\begin{equation}
\rho \to \rho'=\mathcal{E}[\rho ]=\sum_{\vec{\alpha}} \tau_{\vec{\alpha}} r_{\vec{\alpha}} \sigma_{\vec{\alpha}},
% \label{Pauli_Map}
\end{equation}
% 
with $-1\leq \tau_{\vec{\alpha}} \leq 1$. 
% 
In this case the density matrix in vector form holds 
% 
\begin{equation}
 \ket{\rho}=\sum_{\vec{\alpha}} r_{\vec{\alpha}} \ket{\sigma_{\vec{\alpha}}},
\end{equation}
% 
where $\ket{\sigma_{\vec{\alpha}}}=\ket{\sigma_{\alpha_1}}\otimes\dots \otimes\ket{\sigma_{\alpha_N}}$, and satisfy the usual orthogonality relation $\braket{{\sigma_{\vec{\alpha}}}}{{\sigma_{\vec{\alpha}'}}} = \tr \left(\sigma_{\vec{\alpha}}^{\dagger} \sigma_{\vec{\alpha}'}\right) = 2^N ~\delta_{\vec{\alpha}\vec{\alpha}'}$.
(Proofs in an appendix using binary indices XD)

@@

\subsection{Parte de Francois}

We have the matrix 
\begin{equation}
\sa=\left(
\begin{array}{cccc}
1 &1 &1   &1   \\
 1 & 1  & -1&-1   \\
1  & -1  & 1 & -1\\
1&-1&-1&1  
\end{array}
\right)=\frac12\sa^{-1}.
\label{eq:1}
\end{equation}
and further define the matrix
\begin{equation}
\san=\left(\sa\right)^{\otimes N}
\label{eq:1a}
\end{equation}
% }}}
\subsection{A vector space of channels} % {{{
% \begin{itemize} % {{{ Cosas por escribir aca
% \item Canales PCE como espacios vectoriales \todo{Francois escribe}
% \item Regla de $2^k$
% \item Tamaño de las diferentes clases que borran un numero fijo de componentes
% y tambien nota de qeu son igual entre complementarios: computo del numero de
% bases dada una dimension de subespacios vectoriales, aqui entra la formula del
% binomial-q. \todo{Esperemos que evolucione mas el articulo y luego vemos que ponemos}
% \item Intento de identificar elementos, aka hermanistos PCE \cpnote{Esto dependerá de si sale algo interesante,}: De entrada aqui se tiene que mencionar minimo la identificacion del tamaño de las clases.
% \item \ddnote{Agrego esto:} A final remarks of the derivation as a tool.
% Concepts might be complicated, but the tool gives some simple rules to the
% reader: \textit{tell me what components you want to keep, and the (vector)
% summation rules will give you the rest of components to make the target
% operation a CPTP one.}
% \end{itemize} % }}}

We look for those vectors $\vec\tau$ consisting of 0's and 1's such that 
\begin{equation}
\san\vec\tau=2^N\vec p
\label{eq:3}
\end{equation}
where $\vec p$ is a vector with positive entries. Here $\vec\tau$ is a $4^N$ dimensional vector of 0's
and 1's. We number the entries of $\vec\tau$ 
by the multi-indices $\vec\alpha=(\alpha_1,\ldots,\alpha_N)$ where $0\leq\alpha_k\leq3$.
The entries of the positive vector are given by $2^Np_{\vec\alpha}$. It then follows that 
the expression (\ref{eq:3}) satisfies
\begin{equation}
\left(
\san_{\vec\alpha\vec\beta}
\right)
\tau_\beta=2^Np_{\vec\alpha}
\label{eq:4}
\end{equation}
where
\begin{equation}
\left(
\san_{\vec\alpha\vec\beta}
\right)=\sa_{\alpha_1\beta_1}\cdot\ldots\cdot \sa_{\alpha_N\beta_N}
\label{eq:5}
\end{equation}

From (\ref{eq:4}) immediately follows, via (\ref{eq:1})
\begin{equation}
\tau_\alpha=\left(
\san_{\vec\alpha\vec\beta}
\right)p_\beta
\label{eq:6}
\end{equation}
which we analyze iteratively. We shall essentially use the fact that
\begin{equation}
p_{\vec\alpha}+p_{\vec\beta}=0\quad\Leftrightarrow\quad p_{\vec\alpha}=p_{\vec\beta}=0
\label{eq:7}
\end{equation}

Now we need a definition: to each multi-index $\vec\alpha$ we associate a {\em set\/}
of multi-indices $\Phi(\vec\alpha)$ as follows
\begin{equation}
\Phi(\vec\alpha):=\left\{
\vec\beta:\san_{\vec\alpha\vec\beta}=1
\right\}=\left\{
\vec\beta:
\sa_{\alpha_1\beta_1}\cdot\ldots\cdot \sa_{\alpha_N\beta_N}
=1
\right\}
\label{eq:8}
\end{equation}
If we now assume that $\tau_{\vec\alpha}=1$, it follows from subtracting the two combined equations
\begin{subequations}
\begin{eqnarray}
\sum_{\vec\beta}p_{\vec\beta}&=&1
\label{eq:9a}\\
\sum_{\vec\beta}\san_{\vec\alpha\vec\beta}p_{\vec\beta}&=&\tau_{\vec\alpha}=1
\end{eqnarray}
\label{eq:9}
\end{subequations}
that for all $\vec\beta\notin\Phi(\vec\alpha)$
\begin{eqnarray}
p_{\vec\beta}=0.
\label{eq:10}
\end{eqnarray}
Thus, if $\tau_{\vec\alpha}=1$, then $\tau_{\vec\gamma}$
and $\tau_{\vec{\gamma^\prime}}$ are equal if, for all $\vec\beta\in\Phi(\vec\alpha)$.
\begin{equation}
\san_{\vec\beta\vec\gamma}=\san_{\vec\beta\vec{\gamma^\prime}}
\label{eq:11}
\end{equation}
holds for all $\vec\beta\in\Phi(\vec\alpha)$. This follows from (\ref{eq:6}) as well as the fact that, due 
to (\ref{eq:10}), we only need sum over $\vec\beta\in\Phi(\vec\alpha)$.

% If this condition is fulfilled and $\tau_{\vec\alpha}=1$, then
%\begin{subequations}
%\begin{eqnarray}
%\tau_{\vec\gamma}&=&\sum_{\vec\beta}\left(
%M^{\otimes N}
%\right)_{\vec\beta\vec\gamma}p_{\vec\beta}
%\label{eq:10na}
%\\
%&=&\sum_{\vec\beta\in\Phi(\vec\alpha)}\left(
%M^{\otimes N}
%\right)_{\vec\beta\vec\gamma}p_{\vec\beta}
%\label{eq:10nb}
%\\
%&=&\sum_{\vec\beta\in\Phi(\vec\alpha)}\left(
%M^{\otimes N}
%\right)_{\vec\beta\vec{\gamma^\prime}}p_{\vec\beta}
%\label{eq:10nc}
%\\
%&=&\sum_{\vec\beta}\left(
%M^{\otimes N}
%\right)_{\vec\beta\vec{\gamma^\prime}}p_{\vec\beta}
%\label{eq:10nd}
%\\
%&=&\tau_{\vec{\gamma^\prime}}
%\label{eq:10ne}
%\end{eqnarray}
%\label{eq:10n}
%\end{subequations}
%Here the transition from (\ref{eq:10na}) to (\ref{eq:10nb}) follows from (\ref{eq:10}), from (\ref{eq:10nb}) to (\ref{eq:10nc})
%follows from (\ref{eq:11}), from (\ref{eq:10nc}) to  (\ref{eq:10nd}) follows again from (\ref{eq:10}).

Condition (\ref{eq:11}) therefore connects three multi-indinces, $\vec\alpha$, $\vec\gamma$ and $\vec{\gamma^\prime}$.
When such a connection exists, $\tau_{\vec\alpha}=1$ implies 
$\tau_{\vec\gamma}=\tau_{\vec{\gamma^\prime}}$. Let us now work out the nature of this connection.

Since $\sa_{\alpha\beta}=\pm1$, we may rewrite (\ref{eq:11}) as
\begin{equation}
\sa_{\beta_1\gamma_1}\sa_{\beta_1\gamma_1^\prime}\cdot\ldots\cdot \sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=1.
\label{eq:12}
\end{equation}
This must hold for all $\vec\beta\in\Phi(\vec\alpha)$. From this follows that (\ref{eq:12}) may be rewritten as
\begin{equation}
\sa_{\beta_1\gamma_1}\sa_{\beta_1\gamma_1^\prime}\cdot\ldots\cdot \sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=
\sa_{\alpha_1\beta_1}\cdot\ldots\cdot \sa_{\alpha_N\beta_N}.
\label{eq:13}
\end{equation}
Since this must hold for all $\vec\beta\in\Phi(\vec\alpha)$, it follows that 
the above relation must hold individually for every index. Thus we have, 
that, for all $1\leq k\leq N$, $\gamma_k$
and $\gamma_k^\prime$ are connected by
\begin{equation}
\sa_{\beta\gamma_k}\sa_{\beta\gamma_k^\prime}=\sa_{\beta\alpha}
\label{eq:14}
\end{equation}
for all $0\leq\beta\leq3$. This is equivalently expressed as 
\begin{equation}
\gamma_k^\prime=\alpha\oplus{}\gamma_k
\label{eq:15}
\end{equation}
where the $\oplus{}$ operation is defined by (\ref{eq:14}). See Figure \ref{tab:1} for a detailed description.

\begin{figure}
\begin{center}
\begin{tabular}{| c | c c c c |}
\hline
$\oplus{}$ & 0 & 1& 2 & 3\\
\hline
0 & 0 & 1 & 2 & 3\\
1 & 1 & 0 & 3 & 2\\
2 & 2 & 3 & 0 & 1 \\
3 &3 & 2 & 1 & 0\\
\hline
\end{tabular}
\caption{Table for the $\oplus{}$ operation defined in (\ref{eq:14}). Note that the operation
is an {\em abelian group}, in fact it corresponds to the {\em Klein group}, where the
neutral element is $0$. This is the reason for choosing an additive notation for the operation
defined in (\ref{eq:14}).
}
\label{tab:1}
\end{center}
\end{figure}

Note further that if we perform the identification
\begin{subequations}
\begin{eqnarray}
0&\to&(0,0)\label{eq:identa}\\
1&\to&(0,1)\label{eq:identb}\\
2&\to&(1,0)\label{eq:identc}\\
3&\to&(1,1)\label{eq:identd}
\end{eqnarray}
\label{eq:ident}
\end{subequations}
then the $\oplus$ operation reduces to simple vector addition in
binary arithmetic. If we therefore denote by $\overline{\alpha}$
the multi-index $\vec\alpha$ converted to a binary vector by the componentwise application of (\ref{eq:ident}),
the connection between $\vec\alpha$, $\vec\gamma$, and $\vec{\gamma^\prime}$ defined by (\ref{eq:11}) is rewritten 
as
\begin{equation}
\overline\gamma=\overline\alpha+\overline{\gamma^\prime}
\label{eq:17}
\end{equation}
where the addition sign here refers to ordinary binary vector addition.

From this readily follows an amusing property: the set of all multi-indices $\overline\gamma$
for which $\tau_{\overline\gamma}=1$\cpnote{I guess instead of overline, we want 
to use arrow, or this denotes something else?}, is closed under binary vector addition, in other words, it
forms a {\em vector subspace\/} of the set of all multi-indices. Indeed, let
$\overline\alpha$ and $\overline\gamma$ belong to that set. Then if 
\begin{equation}
\overline{\gamma^\prime}=\overline\alpha+\overline\gamma
\label{eq:14b}
\end{equation}
then by the preceding considerations, $\tau_{\overline\gamma^\prime}$ is equal to $\tau_{\overline\gamma}$
and thus equal to one.

So we may now proceed to generate all solutions: we start out from the solution having $\tau_{\vec0}=1$, with
everything else $0$. We may then successively switch $\tau$'s to $1$ for various values of $\vec\alpha$, 
taking care immediately to set equal to one the values of $\tau$ that correspond to values of $\vec\beta$
generated by the previously switched values of $\vec\alpha$ via (\ref{eq:11}).

A moment's consideration will further show that the above reasoning can be inverted, that is, that if we
set all $\tau_{\overline\gamma}$ equal to one whenever the $\overline\gamma$ belong to a given vector 
subspace of the set of all indices, then the vector $\vec\tau$ indeed has an image which is a vector with 
only positive components.

%Now everything follows with delightful simplicity. First extend the $\oplus{}$ operation to vectors 
%componentwise
%\begin{equation}
%\vec\alpha\oplus{}\vec\beta=(\alpha_1\oplus{}\beta_1,\ldots,\alpha_N\oplus{}\beta_N).
%\label{eq:16}
%\end{equation}
%Remark, as a useful fact, that the inverse under $\oplus$ of any number $\alpha$ is $\alpha$ itself.

%If $\tau_{\vec\alpha}=1$, then it follows from the above that 
%for all $\gamma$
%\begin{equation}
%\tau_{\vec\gamma}=\tau_{\vec\alpha\oplus{}\vec\gamma}.
%\label{eq:17}
%\end{equation}

%Now take an arbitrary $\vec{\alpha}_1$ and set $\tau_{\vec{\alpha}_1}=1$. This immediately imposes the
%relationship
%\begin{equation}
%\tau_{\vec\gamma}=\tau_{\alp1\oplus{}\vec\gamma}
%\label{eq:18}
%\end{equation}
%which to every $\vec\gamma$ assigns exactly one other multi-index such that the corresponding values of $\tau$
%must be equal. Note that (\ref{eq:18}) is vacuous when applied to $\gamma=\alp1$: indeed $\alp1\oplus\alp1=\vec0$,
%and $\tau_{\vec0}$ is one by convention. 
%
%Now choose another multi-index, say $\alp2$, which is not equal to $\alp1$, nor to any site
%that is automatically equal to $\tau_{\alp1}$. Set $\tau_{\alp2}=1$. We obviously must also set $\tau_{\alp2\oplus\alp1}=1$,
%since the two are equal because of (\ref{eq:18}). By the same reasoning that led to (\ref{eq:18}), we now find that 
%\begin{equation}
%\tau_{\vec\gamma}=\tau_{\alp1\oplus{}\vec\gamma}=\tau_{\alp2\oplus{}\vec\gamma}=\tau_{\alp1\oplus\alp2\alp2\oplus{}\vec\gamma}
%\label{eq:19}
%\end{equation}
%Thus we find that the $\tau$'s are now constant over domains of $4$, as opposed to $2$ previously, when only one
%single $\vec\alpha$, namely $\alp1$, had been fixed to have $\tau_{\alp1}=1$. Further, it follows from the group property
%of $\oplus$ that the different domains are {\em disjoint}. The 3 multi-indices associated to a given $\vec\gamma$ are never associated
%to any other $\vec{\gamma^\prime}$. 
%
%After adding $\alp1$, we have at least 2 sites equal to 1, after adding $\alp2$, we have 4: $\vec0$, $\alp1$, $\alp2$, and $\alp1+\alp2$. 
%Clearly, at each addition, the total number doubles. This shows the $2^k$ rule. 
%
%How far can this process go? Well, the total number of multi-indices is $4^N$, so this can go on until $2\cdot4^{N-1}$ sites are occupied,
%in other words, we may double $2N-1$ times.
%
%Now to show that the maximal solutions are generators, that is, that all solutions can be expressed as intersections of maximal 
%solutions, that is, solutions with $2\cdot4^{N-1}$ 1's. Any maximal solution can be obtained by the successive adjunction
%of $\alp1, \alp2,\ldots,\alp{2N-1}$. Again, due to the group property, the final solution generated does not depend on the order
%of the $\alp{k}$. 
%
%Now let us consider a solution with half the number of elements of a maximal solution, that is, one generated by $\alp1, \alp2,\ldots,\alp{2N-2}$. 
%At this stage, the $\tau_{\vec\alpha}$ are constant over domains of size $4^{N-1}$ and there are a total of $4^{N-1}$ 1's. 
%There are thus 2 inequivalent remaining domains where I could put the final $\alp{2N-1}$. These 2 different choices yield disjoint
%maximal solutions, the intersection of which yields the solution with half the number of elements of the maximal solution. 
%Every solution one step away from maximal can thus be expressed (uniquely) as the intersection of 2 maximal solutions. 
%
%Arguing inductively backwards, the same result can be shown for arbitrary solutions. We therefore have shown both the $2^k$ 
%rule and the fact that all solutions are expressible uniquely as intersections of maximal solutions.

The dimension of the vector space $V$ of all multi-indices is $2N$, and we have seen earlier that
\begin{equation}
W=\left\{
\vec\alpha:\vec\alpha\in V, \tau_{\vec\alpha}=1
\right\}
\label{eq:19}
\end{equation}
is a subspace of $V$. As such, $W$ has a given dimension $K$, which means that $W$ has $2^K$ elements. In other words,
a vector $\vec\tau$ with the property discussed above can only have $2^K$ elements equal to 1, for a given integer $K$.

By standard theorems of linear algebra, any subspace $W$ can be extended to a maximal (non-trivial) subspace of dimension
$2N-1$ by adjoining appropriate additional basis elements. This can clearly be done in different ways. We therefore arrive to
the set of maximal extensions of $W$. Clearly, the intersection of all the elements of this set reduces to $W$ itself, leading to
the result that all PCE's can be obtained as intersections of maximal PCE's.

\ddnote{Agrego esto:} A final remarks of the derivation as a tool. Concepts might be complicated, but the tool gives some simple rules to the reader: \textit{tell me what components you want to keep, and the (vector) summation rules will give you the rest of components to make the target operation a CPTP one.}

@@

>>>>

We now turn to find the matrix form of the map $\mathcal{E}$ in order to construct the Choi matrix and the conditions the set of parameters $\{\tau_{\alpha}\}$ need to satisfy in order to $\mathcal{E}$ be considered a quantum channel. By writing the density matrix in vector form $\ket{\rho}=\sum_{\alpha=0}^{3} \alpha_{\alpha} \ket{\sigma_{\alpha}}$, it is easy to show that the matrix form of the map $\mathcal{E}$ may be written as
% 
\begin{equation}
\hat{\mathcal{E}} = \frac{1}{2}\sum_{\alpha=0}^{3} \tau_{\alpha} \dyad{\sigma_{\alpha}},
% \label{Map_Pauli}
\end{equation}
%
where the kets $\ket{\sigma_{\alpha}}$ correspond to the vectorized elements of
the Pauli basis and satisfy the usual relation $
\braket{{\sigma_{\alpha}} }{{\sigma_{\alpha'} }} = \tr \left(\sigma_{\alpha}^{\dagger} \sigma_{\alpha'}\right) = 2
~\delta_{\alpha\alpha'}$. After some steps it is possible to show that the
associated Choi matrix reads
% 
\begin{equation}
 \mathcal{D} = \frac{1}{2}\sum_{\alpha=0}^{3} \tau_{\alpha} \sigma_{\alpha} \otimes \sigma_{\alpha}^*.
%  \label{Choi_1}
\end{equation}
% 
Note that $\mathcal{D}$ has the same form as the matrix representation of a random unitary channel whose Kraus operators are given by $K_{\alpha}=\sqrt{\frac{\tau_{\alpha}}{2}}\sigma_{\alpha}$. For the latter case, it has been shown that corresponding eigenvalues read \cite{CHRUSCINSKI20131425}
% 
\begin{equation}
 \lambda_{\beta} = \frac{1}{2}\sum_{\alpha=0}^3H_{\beta\alpha}^{(4)}\tau_{\alpha},
\end{equation}
%
or
% 
\begin{equation}
 \vec{\lambda} = \frac{1}{2}~ H^{(2)}\otimes H^{(2)}\vec{\tau},
\end{equation}
% 
where $H^{(m)}$ is the Hadamard matrix of order \textit{m}, and for $m=2$ reduces to the usual Hadamard matrix.
% 
\begin{equation}
 H^{(2)}=\begin{pmatrix}
        1 & 1\\
        1 & -1\\
    \end{pmatrix}.
 \label{Hadd_Mat}
\end{equation}

@@

\subsubsection{$N$ qubits}
% 
For the case of $N$ qubits, the density matrix may be written as
% 
\begin{equation}
\rho=\sum_{\vec{\alpha}} r_{\vec{\alpha}} \sigma_{\vec{\alpha}}.
% \label{rho2}
\end{equation}
% 
Analogously to the single qubit case, we can define a $N$-qubits Pauli map
% 
\begin{equation}
\rho \to \rho'=\mathcal{E}[\rho ]=\sum_{\vec{\alpha}} \tau_{\vec{\alpha}} r_{\vec{\alpha}} \sigma_{\vec{\alpha}},
% \label{Pauli_Map}
\end{equation}
% 
with $-1\leq \tau_{\vec{\alpha}} \leq 1$. 
% 
In this case the density matrix in vector form holds 
% 
\begin{equation}
 \ket{\rho}=\sum_{\vec{\alpha}} r_{\vec{\alpha}} \ket{\sigma_{\vec{\alpha} }},
\end{equation}
% 
where $\ket{\sigma_{\vec{\alpha} }}=\ket{\sigma_{\alpha_1}}\otimes\dots \otimes\ket{\sigma_{\alpha_N}}$, and satisfy the usual orthogonality relation $\braket{{\sigma_{\vec{\alpha} } }}{{\sigma_{\vec{\alpha}'} }} = \tr \left(\sigma_{\vec{\alpha}}^{\dagger} \sigma_{\vec{\alpha}'}\right) = 2^N ~\delta_{\vec{\alpha}\vec{\alpha}'}$.
(Proofs in an appendix using binary indices XD)

@@

@@

\input{vector_space}
